---
title: "Who does more pushups"
author: "your name"
date: "March 8"
output:
  html_document: default
  word_document: default
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

Several years ago some MAT 111 students who were on the footbal team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

```{r eval=FALSE}
data(pushups)
View(pushups)
help(pushups)
```
The data frame has 3 columns: weight, pushups and postitons.

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of runninga and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?
  
I see that the data frame has 3 columns: weight, pushups and postitons. I will use this information to answer the question.
  


# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

I will use a boxplot for the graphical method and R-function favstats to do the numerical method.


# Results
<!--You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.!-->

My graphical and numerical results were similar. The boxplot showed that the skill players do an average of 45 pushups, and the line players do an average of 15 pushups and the numerical table showed that line players do an average of 14.5 pushups and skill players do an average of 47.5 pushups.


## Graphical Results
<!--Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.!-->


```{r}
a <- ggplot(pushups, aes(x=position, y=pushups, col=position))
a + geom_boxplot()
```


According to this graph, the skill players do an average of 45 pushups, and the line players do an average of 15 pushups.

## Numerical Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=pushups)
```
According to this table, line players do an average of 14.5 pushups and skill players do an average of 47.5 pushups.


# Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

Hypothesis: I believe that skill players will do more pushups than line players.
This hypothesis was correct because the boxplot and numerical table shows that the skill players do a higher number of pushups than the skill players. I thought this would be true originally because the data frame lists the pushups in columns and before I ran any  tests, it looked like the skill players numbers were higher. For example, one skill did 98 pushups and the line player below him did 11 pushups.

```{r}

t.test(pushups~position, data=pushups)


```
According to the t.test the p-value is so low that there is no way the # of pushups between line and skill players could be close.

# Discussion and Conclusion
<!--State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.!-->

According to the information in the charts above, skill players do more pushups than line players. They do around 30 more pushups than the line players on average.
